WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-08-14 ms.tex
Add Holz citation

>>>>

On the topic of very low\nobreakdashes-latency localization, we also recommend Chen~\&~Holz (in preparation), who propose a rapid localization scheme that is similar to ours, but even faster: their likelihood is strictly Gaussian, so one more marginalization integral (the integral over arrival time) can be performed analytically.
